Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
split the fig of the first CEK

%	Continuation typing \fbox{$ \kappa : T_1 \Longrightarrow T_2 $}
%	\begin{gather*}
%	\dots \quad
%	\inference{
%		c : T_1 \Longrightarrow T_2 &
%		\kappa : T_2 \Longrightarrow T_3
%	}{
%		\langle c \rangle \kappa : T_1 \Longrightarrow T_3
%	}
%	\end{gather*}

@@

	\caption{CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} cast 
	calculus}
	\label{machine-cekc}
\end{figure}

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines \citep{felleisen1986control}.
\todo[inline]{Briefly present the main ideas regarding how a CEK
  machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Use citep to put a citation in parentheses, as I've
  done above. -Jeremy }
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy
\\---\\
Could you tell me why taking the value first is better?
I am always taking the target of induction/match first. -KC}
We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

>>>>

	\caption{Syntax of CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} 
	cast calculus}
\label{machine-cekc-syntax}
\end{figure}

\begin{figure}
%	Continuation typing \fbox{$ \kappa : T_1 \Longrightarrow T_2 $}
%	\begin{gather*}
%	\dots \quad
%	\inference{
%		c : T_1 \Longrightarrow T_2 &
%		\kappa : T_2 \Longrightarrow T_3
%	}{
%		\langle c \rangle \kappa : T_1 \Longrightarrow T_3
%	}
%	\end{gather*}

@@

	\caption{Reduction rules of CEK abstract machine ($ \mathcal{D} $) for the 
	\lazyD{} cast calculus}
	\label{machine-cekc-reduction}
\end{figure}

Fig.~\ref{machine-cekc-syntax} defines the syntax of a CEK machine 
\citep{felleisen1986control} evaluating 
the \lazyD{} cast calculus.
\todo[inline]{Briefly present the main ideas regarding how a CEK
  machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Use citep to put a citation in parentheses, as I've
  done above. -Jeremy }
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy
\\---\\
Could you tell me why taking the value first is better?
I am always taking the target of induction/match first. -KC}
We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.
